An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-12-25 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Article updates.

The LINEX model coefficients $a_0$ and $c_t$ imply time-varying
values of $\alpha$, $\beta$, and $\gamma$ as shown by \citet[Equations~7]{Warr:2012cg}.
Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
We found unconstrained fitting produced $\alpha$,$\beta$,$\gamma$ trajectories
that violated parameter constraints ($[0,1]$) for all countries, with the exception of Iran.
If the LINEX model were forced to respect the constraints,
it would fit worse than it already does for those countries where
the constraints are violated (that is, for every country except Iran).
\citet{Warr:2012cg} selected values of $a_0$ and $c_t$, while still holding them constant
for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
were respected throughout their time series.
But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
Because in our results unconstrained LINEX models already fit worse than 
constrained Cobb-Douglas and CES models,
we chose to report unconstrained LINEX model fits in this paper.

@@

**** Shall we have a section here discussing which function is ``best''? --MKH ****
What are the criteria?

@@

Best match to historical data: CES.

@@

Our assessment: None of the production functions is perfect. 
Probably CD is best compromise among ease of estimating, good (but not best) fit to historical data, and
small uncertainties in fitted parameters.

@@

>>>>

The LINEX model coefficients $a_0$ and $c_t$ imply time-varying
values of $\alpha$, $\beta$, and $\gamma$ as shown by \citet[Equations~7]{Warr:2012cg}.
Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
We found unconstrained fitting produced $\alpha$, $\beta$, $\gamma$ trajectories
that violated parameter constraints ($[0,1]$) for all countries, with the exception of Iran.
If the LINEX model were forced to respect the constraints,
it would fit worse than it already does for those countries where
the constraints are violated (that is, for every country except Iran).
\citet{Warr:2012cg} selected values of $a_0$ and $c_t$, while still holding them constant
for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
were respected throughout their time series.
But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
Because in our results unconstrained LINEX models already fit worse than 
constrained Cobb-Douglas and CES models,
we chose to report unconstrained LINEX model fits in this paper.

@@

**** Shall we have a section here discussing which function is ``best''? --MKH ****
Here is a first cut at some criteria and a recommendation.

@@

Best match to historical data: CES. But CD is close. LinEx struggles.

@@

Easy to respect constraints during fitting process: CD and CES easy. LinEx difficult.

Our assessment: None of the production functions is perfect. 
Probably CD is best compromise among ease of estimating, good (but not best) fit to historical data, and
small uncertainties in fitted parameters. 
If precise fitting to historical data is paramount (and you're unconcerned about uncertainties
in fitted coefficients), CES is the best.

@@

Maybe put the discussion of ``Which production function is best'' here?
